\documentclass{article}
\usepackage{amsmath}
\usepackage{hyperref}

\title{Terms of Service}
\date{}

\begin{document}
\maketitle

\section*{Introduction}
Welcome to [Lucy]! By using our Discord bot, you agree to these Terms of Service (``Terms''). Please read them carefully.

\section*{1. Acceptance of Terms}
By accessing or using [Lucy], you agree to be bound by these Terms. If you do not agree to these Terms, please do not use the bot.

\section*{2. Use of the Bot}
You may use [Lucy] only in compliance with these Terms and all applicable local, state, national, and international laws, rules, and regulations.

\subsection*{2.1 Age Requirement}
You must be at least 13 years old to use [Lucy]. If you are under 18, you must have your parent or guardian’s permission to use the bot.

\subsection*{2.2 License}
We grant you a non-exclusive, non-transferable, revocable license to use [Lucy] for your personal, non-commercial use.

\section*{3. Prohibited Uses}
You agree not to use [Lucy] to:
\begin{itemize}
    \item Engage in any unlawful or fraudulent activity.
    \item Harass, abuse, or harm another person or group.
    \item Share or transmit any inappropriate, offensive, or illegal content.
    \item Disrupt or interfere with the normal operation of the bot or Discord.
    \item Reverse engineer, decompile, or disassemble the bot.
\end{itemize}

\section*{4. Privacy}
We respect your privacy. Please review our Privacy Policy, which also governs your use of [Lucy], to understand our practices.

\section*{5. Content}
You are responsible for the content you post using [Lucy].
We do not endorse, support, represent, or guarantee the completeness, truthfulness, accuracy, or reliability of any content posted via the bot.

\section*{6. Termination}
We may suspend or terminate your access to [Lucy] at any time, without prior notice or liability, for any reason, including if you breach these Terms.

\section*{7. Disclaimer of Warranties}
[Lucy] is provided ``as is'' and ``as available'' without any warranties of any kind, either express or implied.
We do not guarantee that the bot will be uninterrupted, error-free, or free of viruses or other harmful components.

\section*{8. Limitation of Liability}
In no event shall we be liable for any indirect, incidental, special, consequential, or punitive damages arising out of your use of [Lucy].

\section*{9. Changes to the Terms}
We reserve the right to modify these Terms at any time. We will notify you of any changes by posting the new Terms on our website or through the bot.
Your continued use of the bot after such changes have been made will constitute your acceptance of the new Terms.

\section*{10. Governing Law}
These Terms are governed by and construed in accordance with the laws of [Michigan, USA], without regard to its conflict of law principles.

\section*{11. Contact Information}
If you have any questions about these Terms, please contact us at [Brandon Graham Cobb].

\bigskip
\begin{center}
    \textbf{[Lucy]} \\
    \textbf{[Brandon Graham Cobb]}
\end{center}

\end{document}
